Inducing Domain Specific Languages for Bayesian Program Learning

### 2018-02-01 paper.tex
tiny dsl table change

\begin{table}
\centering
\begin{tabular}{| l | l |}
  \hline
  \emph{name} & \emph{type} \\
  \hline
    empty & \texttt{[$\alpha$]} \\
    singleton & \texttt{$\alpha$ $\rightarrow$ [$\alpha$]} \\
    range & \texttt{int $\rightarrow$ [int]} \\
    concat & \texttt{[$\alpha$] $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
    map & \texttt{($\alpha$ $\rightarrow$ $\beta$) $\rightarrow$ [$\alpha$] $\rightarrow$ [$\beta$]} \\
    reduce & \texttt{($\beta$ $\rightarrow$ $\alpha$ $\rightarrow$ $\beta$) $\rightarrow$ $\beta$ $\rightarrow$ [$\alpha$] $\rightarrow$ $\beta$} \\
    \hline
    true & \texttt{bool} \\
    not & \texttt{bool $\rightarrow$ bool} \\
    and & \texttt{bool $\rightarrow$ bool $\rightarrow$ bool} \\
    or & \texttt{bool $\rightarrow$ bool $\rightarrow$ bool} \\
    \hline
    0, $\ldots$, 9 & \texttt{int} \\
    + & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    * & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    negate & \texttt{int $\rightarrow$ int} \\
    mod & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    eq? & \texttt{int $\rightarrow$ int $\rightarrow$ bool} \\
    gt? & \texttt{int $\rightarrow$ int $\rightarrow$ bool} \\
    is-prime & \texttt{int $\rightarrow$ bool} \\
    is-square & \texttt{int $\rightarrow$ bool} \\
    sort & \texttt{[int] $\rightarrow$ [int]} \\
    \hline
    sum & \texttt{[int] $\rightarrow$ int} \\
    reverse & \texttt{[$\alpha$] $\rightarrow$ [$\alpha$]} \\
    all & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool} \\
    any & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool} \\
    index & \texttt{int $\rightarrow$ [$\alpha$] $\rightarrow$ $\alpha$} \\
    filter & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
    slice & \texttt{int $\rightarrow$ int $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
  \hline
\end{tabular}
\caption{DSL for the domain of list function.}
\label{listdsl}
\end{table}

>>>>

\begin{table}
\centering
\begin{tabular}{| l | l |}
  \hline
  \emph{name} & \emph{type} \\
  \hline
    empty & \texttt{[$\alpha$]} \\
    singleton & \texttt{$\alpha$ $\rightarrow$ [$\alpha$]} \\
    concat & \texttt{[$\alpha$] $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
    map & \texttt{($\alpha$ $\rightarrow$ $\beta$) $\rightarrow$ [$\alpha$] $\rightarrow$ [$\beta$]} \\
    reduce & \texttt{($\beta$ $\rightarrow$ $\alpha$ $\rightarrow$ $\beta$) $\rightarrow$ $\beta$ $\rightarrow$ [$\alpha$] $\rightarrow$ $\beta$} \\
    \hline
    true & \texttt{bool} \\
    not & \texttt{bool $\rightarrow$ bool} \\
    and & \texttt{bool $\rightarrow$ bool $\rightarrow$ bool} \\
    or & \texttt{bool $\rightarrow$ bool $\rightarrow$ bool} \\
    \hline
    0, $\ldots$, 9 & \texttt{int} \\
    + & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    * & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    negate & \texttt{int $\rightarrow$ int} \\
    mod & \texttt{int $\rightarrow$ int $\rightarrow$ int} \\
    eq? & \texttt{int $\rightarrow$ int $\rightarrow$ bool} \\
    gt? & \texttt{int $\rightarrow$ int $\rightarrow$ bool} \\
    is-prime & \texttt{int $\rightarrow$ bool} \\
    is-square & \texttt{int $\rightarrow$ bool} \\
    range & \texttt{int $\rightarrow$ [int]} \\
    sort & \texttt{[int] $\rightarrow$ [int]} \\
    \hline
    sum & \texttt{[int] $\rightarrow$ int} \\
    reverse & \texttt{[$\alpha$] $\rightarrow$ [$\alpha$]} \\
    all & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool} \\
    any & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ bool} \\
    index & \texttt{int $\rightarrow$ [$\alpha$] $\rightarrow$ $\alpha$} \\
    filter & \texttt{($\alpha$ $\rightarrow$ bool) $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
    slice & \texttt{int $\rightarrow$ int $\rightarrow$ [$\alpha$] $\rightarrow$ [$\alpha$]} \\
  \hline
\end{tabular}
\caption{DSL for the domain of list function.}
\label{listdsl}
\end{table}
